### 2023-01-17 Documentation/UFMG/Relatorio_2/Summary/Summary.tex

@@

>>>>

The setup used for this project can be seen in the Figure 2. To run the experiment automatically it is used a computational processing machine to integrate the peripherals and run their routines, system sensors such as the oscilloscope and the high speed camera 
and also the system actuators which is represented by the high voltage power supply and the syringe pump.

@@

The algorithms implemented in the computer machine was developed in python by another student and it is already collecting data and classifying the spraying dynamics.
In Figure 3 and Figure 4 shows pictures took by the high speed camera of some of the possible spraying dynamics we can reach. The videos took by the camera is not being used in the classification
algorithm. It is used for manual validation of it.
